---
title: "Vargas_Project_01"
author: "Juan Vargas"
date: "10/9/2022"
output: 
  html_document:
      toc: true
      toc_float: true
      toc_depth: 4
editor_options: 
  chunk_output_type: console
---

# Reproducible Reporting


## Load libraries

```{r}
library(tidyverse)
library(kableExtra)
library(DT)
```



## Funcitons 

```{r}

freezer = function(){
  setwd('C:\\Users\\Juan\\Documents\\Vargas_Project_01\\Raw Data')
}

fridge = function(){
  setwd('C:\\Users\\Juan\\Documents\\Vargas_Project_01\\Processed Data')
}

reports = function(){
  setwd('C:\\Users\\Juan\\Documents\\Vargas_Project_01\\Reports')
}

```


## Report



Exposure to high levels of lead may cause anemia, weakness, and kidney and brain damage. Lead can cross the placental barrier, which means pregnant women who are exposed to lead also expose their unborn child. Lead can damage a developing baby's nervous system.

The data was collected by a team of researchers led by the CDC, in which investigates children from the ages of 3 and 15 in El Paso living in different distances from a lead-emitting ore smelter.
We will be analyzing the lead dataset to determine if living near or far from the smelter affects IQ.




<br>

```{r}
freezer()

dt=
  read_csv('lead-iq-01.csv')

datatable(dt)
```

<br>


```{r}
summary(dt)


```


Changing the outlier

```{r}
dt %>% filter(IQ > 900)

# Its only 1 row, so we can work on it as if theres more

dt$IQ = ifelse(dt$IQ == 999, 99,dt$IQ)
```


```{r}
fridge()

write_csv(dt,'lead-iq-01-outlier_removed.csv')

```



## Plot, Histogram

```{r}

dt %>%
  ggplot() +
    geom_histogram(aes(x = IQ, fill = Smelter), alpha = 0.7) +
    scale_fill_manual(values = c("#69b3a2", "#404080")) +
  ggtitle('Histogram of IQ between those living Far and Near from the Smelter') +
  labs('Distance')
  

```

Plotted is the histogram of both groups overlapped. We can see those far have a wide range compared to those neat the smelter.

<br>

## Summary table

<br>

The following table is the summary statistics of the data.

<br>

```{r}
dt %>%
  group_by(Smelter) %>%
    summarize(
      'N'= n(),
      'Mean IQ' = mean(IQ),
      'Median IQ' = median(IQ),
      '10% IQ Quantile' = quantile(IQ, probs = 0.10),
      '90% IQ Quantile' = quantile(IQ, probs = 0.90),
      'Max' = max(IQ),
      'Min' = min(IQ)
    ) %>%
  kableExtra::kbl()%>%
  kable_classic_2(full_width = F)

```

 Theres an unusual value of 999 which could be an error.



<br>


Following a t-test will be performed to determine if theres a statistical difference of IQ between of those living far and near from the smelter. Will be using an alpha of 5%

<br>

## T-test

```{r}

t.test(IQ ~ Smelter, data = dt)

```


From the t-test we get t statistic of 1.38 an p-value of 0.1702 failing to reject the null hypothesis, concluding the true difference between the means of IQ between both groups is equal to 0 (95%CI: -1.5118, 8.5058)




