---
title: "Vargas_Project_01"
author: "Juan Vargas"
date: "10/9/2022"
output: 
  html_document:
      toc: true
      toc_float: true
      toc_depth: 4
editor_options: 
  chunk_output_type: console
---

# Reproducible Reporting


## Load libraries

```{r}
library(tidyverse)
library(kableExtra)
library(DT)
```



## Funcitons 

```{r}

freezer = function(){
  setwd('C:\\Users\\Juan\\Documents\\Vargas_Project_01\\Raw Data')
}

fridge = function(){
  setwd('C:\\Users\\Juan\\Documents\\Vargas_Project_01\\Processed Data')
}

reports = function(){
  setwd('C:\\Users\\Juan\\Documents\\Vargas_Project_01\\Reports')
}

```


## Report

<br>

```{r}
freezer()

dt=
  read_csv('lead-iq-01.csv')

datatable(dt)
```

<br>


```{r}
summary(dt)


```



## Plot, Histogram

```{r}

dt %>%
  ggplot() +
    geom_histogram(aes(x = IQ, fill = Smelter), alpha = 0.7) +
    scale_fill_manual(values = c("#69b3a2", "#404080")) +
  ggtitle('Histogram of IQ between those living Far and Near from the Smelter') +
  labs('Distance')
  

```

Plotted is the histogram of both groups overlapped. We can see those far have a wide range compared to those neat the smelter.

<br>

## Summary table

<br>

The following table is the summary statistics of the data.

<br>

```{r}
dt %>%
  group_by(Smelter) %>%
    summarize(
      'N'= n(),
      'Mean IQ' = mean(IQ),
      'Median IQ' = median(IQ),
      '10% IQ Quantile' = quantile(IQ, probs = 0.10),
      '90% IQ Quantile' = quantile(IQ, probs = 0.90),
      'Max' = max(IQ),
      'Min' = min(IQ)
    ) %>%
  kableExtra::kbl()%>%
  kable_classic_2(full_width = F)

```

 Theres an unusual value of 999 which could be an error.



<br>


Following a t-test will be performed to determine if theres a statistical difference of IQ between of those living far and near from the smelter. Will be using an alpha of 5%

<br>

## T-test

```{r}

t.test(IQ ~ Smelter, data = dt)

```


From the t-test we get a p-value of 0.223 failing to reject the null hypothesys, concluding the true difference between the means of IQ between both groups is equal to 0 (95%CI: -10.53844,  44.39128)




